Run aquaculture model for Atlantic salmon

### 2025-12-19 docs-working/07_run_atlantic_salmon_model.qmd
Minor changes to pipeline

Sys.setenv(TAR_PROJECT = "project_farmruns")
farm_IDs_chunked <- tar_read(farm_IDs_chunked, script = farm_script, store = farm_store) %>% unname() %>% unlist()
tar_load(feed_names, script = farm_script, store = farm_store)

tar_load(farm_full_results, script = farm_script, store = farm_store)
total_ends <- bind_rows(lapply(farm_full_results, `[[`, "total_ends"))
cohort_results <- bind_rows(lapply(farm_full_results, `[[`, "cohort_results_daily"))

qsave(total_ends, file.path(output_model_farm_path, "total_ends.qs"))
qsave(cohort_results, file.path(output_model_cohort_path, "cohort_results.qs"))
rm(farm_full_results)
```

>>>>

tar_load(
  farm_full_results,
  store = farm_store
)

total_ends <- bind_rows(lapply(farm_full_results, `[[`, "total_ends"))
cohort_results <- bind_rows(lapply(farm_full_results, `[[`, "cohort_results_daily")) %>% 
  mutate(t = as.integer(t), prod_t = as.integer(prod_t))

qsave(total_ends, file.path(output_path, "total_ends.qs"))
qsave(cohort_results, file.path(output_path, "cohort_results.qs"))

rm(farm_full_results, total_ends, cohort_results)
gc()
```
